Robotic Grasping in Clutter: Using a Hierarchy of Supervisors for \adnote{(Deep)} Learning from Demonstrations\adnote{I would remove deep but if you really want to keep it put it in parens? deep is not central to this and it pigeonholes you}

### 2016-03-18 paper.tex
.

\subsection{DAgger with Supervisor Hierarchy}
Formulating a framework for selecting a supervisor can be difficult because we do not have a known model for how a supervisor selected affects the minimization of the surrogate loss. The reason we do not have a model is because this would require modeling what examples the supervisor will return, the $\theta$ parameters of the neural network policy after training and the states the robot is likely to visit given those parameters.

We could learn a policy using model-free reinforcement learning algorithms ~\cite{sutton1998reinforcement}, where a selection strategy will query different supervisors and learn over time the best supervisor to select given the current policy. However, a problem occurs when applying these approaches because it requires evaluating the objective function, which is the surrogate loss with respect to the costliest and most-skilled supervisor, $S_M$. This requires exhaustively querying the costliest supervisor at each iteration and defeating the purpose of reducing cost.

 In light of this, we propose a greedy allocation strategy, in terms of supervisor cost, where we train a policy with the cheapest supervisor first for a fix number of trials and then advance through the hierarchy training with each supervisor. Our algorithm is as follows: first iterate through Step 1 and 2 of DAgger for a given supervisor, however after iteration $K_m$. Then iterate to the next supervisor in the hierarchy or $m = m+1$.

The number of iterations before advancing to the next supervisor can be challenging to set. In practice, we either advanced when the surrogate loss between supervisors was sufficiently low or when the performance on the grasping in clutter task was not improving. The reason for different options was because some supervisors have very large variance (i.e. crowdsourcing), that a fix threshold on surrogate loss could be misleading without a sufficient number of examples.

>>>>

\subsection{DAgger with Supervisor Hierarchy}
Formulating a framework for supervisor strategy selection poses a challenging problem since no formal model
for the effect of supervisor selection on the surrogate loss minimization is available a priori and since the
neural network policy parameters $\theta$ are additionally changing at each step of DAgger's iterative training process.

While one could consider to learn a policy using model-free reinforcement learning algorithms
~\cite{sutton1998reinforcement}, where a selection strategy will query different supervisors and learn over time the
best supervisor to select given the current policy, this approach requires substantial numbers of 
queries for supervision of the costliest supervisor at each iteration. In light of this, we propose a greedy allocation
strategy.

We train a policy with the cheapest supervisor $S_1$ for a fixed number of $K_1$ iterations with DAgger and then advance
linearly through the hierarchy $S_1, \ldots, S_M$, where the final Neural Network Parameters $\theta_i$ trained using
$S_i$ are transferred iteratively to supervisor $S_{i+1}$ before further training the policy with DAgger.
Each supervisor is trained for $K_i, i\in \{1, \ldots, M\}$ iterations in turn.

While for large numbers of iterations, convergence tests can be applied to determine a point of diminishing return at
which a switch to the next supervisor in the hierarchy can be initiated, this approach can be challenging when only a
limited numbers of roll-outs can be afforded. In practice, we either advanced when the surrogate loss between
supervisors was sufficiently low or when the performance on the grasping in clutter task was not improving empirically. 
For crowdsourcing in particular, we chose the second option since, due to the large variance between demonstrations
we were not able to determine a fixed threshold for the surrogate loss. We hope to significantly scale the number of
training steps in future work to investigate various switching criterea in full detail.
